---
title: "Where Are All the Summer Game Signs?"
subtitle: "Hunting down Ann Arbor's most code-packed streets and neighborhoods in the 2026 AADL Summer Game"
author: "Nick Strayer"
date: 2026-07-01
format:
  html:
    theme: [flatly, summer-game.scss]
    toc: true
    toc-title: "On this page"
    code-fold: true
    code-summary: "Show the code"
    embed-resources: true
    title-block-banner: "#f6a81c"
    title-block-banner-color: "#ffffff"
execute:
  warning: false
  message: false
---

Every summer, lawn signs with secret codes pop up all over Ann Arbor as
part of the library's Summer Game. This year I got curious: if you wanted
to collect as many codes as possible on a single walk, where should you go?
So I pulled the locations of all 2,493 registered signs and went looking
for the answer.

::: {.callout-tip}
## The short version

- **Liberty St** has more signs than any other street in town: **21** of them.
- But the single best *walk* is on the west side: one quarter-mile circle
  around **Duncan St, Circle Dr, and Wines Dr** contains **68 signs** --
  followed closely by the Burns Park area with 67.
- There's an [interactive map](#explore-the-map-yourself) at the bottom if
  you want to scout your own route.
:::

## What's the Summer Game?

The [Ann Arbor District Library Summer Game](https://play.aadl.org) is a
city-wide scavenger hunt: players find codes hidden around town and online,
and redeem the points for prizes. One of the best code sources is **lawn
signs** -- round, colorful signs that players register and put up at their
own homes specifically so other players can find them. The library
publishes a live map of every registered sign at
[aadl.org/summergame/map](https://aadl.org/summergame/map).

That map gets its data from a JSON feed the page loads behind the scenes.
It's not a documented API -- just the map's own data source, which requires
the same AADL login the map does. It lists home signs, participating
businesses, and badge locations; this analysis uses the home signs, which
had **2,493 entries** when I pulled the data on July 1, 2026.

## Which street has the most signs?

The feed doesn't include a clean "street" field -- just a free-text address
like `137 S Wagner Rd<br>Ann Arbor, MI<br>48103`. Since these are typed in
by players, getting a fair street ranking means cleaning up a few things:

- **House numbers** get dropped (`137 S Wagner Rd` becomes `S Wagner Rd`).
- **Directional prefixes** get dropped too, so `N Main St` and `S Main St`
  count as one street instead of two.
- **Apartment numbers and other trailing bits** get trimmed by cutting the
  address off after a recognized street suffix (`Ave`, `St`, `Rd`, `Dr`, ...),
  which handles entries like `4770 Washtenaw Ave a3`.
- A handful of entries (8 of 2,493) put a building name on the first line
  with the real address on the second -- those get detected and re-parsed.

Streets are then counted per city, since names like Liberty, Huron, and
Washington exist in both Ann Arbor and Ypsilanti and shouldn't share a
bucket.

```{r}
#| label: load-and-parse
library(jsonlite)
library(dplyr)
library(ggplot2)

raw <- fromJSON("summer_game_2026_raw.json", simplifyDataFrame = FALSE)

SUFFIXES <- toupper(c("Ave","St","Rd","Dr","Blvd","Ct","Ln","Way","Pl","Cir","Ter",
  "Pkwy","Hwy","Trl","Loop","Path","Row","Sq","Xing","Walk","Run","Bnd","Cv","Grv",
  "Hl","Hls","Knl","Mnr","Pt","Pts","Rdg","Vw","Vlg","Aly","Byp","Cor","Cres","Ext",
  "Gdns","Hts","Jct","Ldg","Mdw","Mdws","Pike","Plz","Spg","Spgs","Sta","Vly","Vis","Grn"))
DIRECTIONS <- c("N","S","E","W","NE","NW","SE","SW")

extract_street <- function(homecode_html) {
  parts <- strsplit(homecode_html, "<br>")[[1]]
  line1 <- parts[1]; line2 <- parts[2]
  street_line <- if (grepl("^\\d", line1)) {
    line1
  } else if (grepl("^\\d", line2)) {
    trimws(strsplit(line2, ",")[[1]][1])
  } else {
    line1
  }
  tokens <- strsplit(trimws(street_line), "\\s+")[[1]]
  if (length(tokens) <= 1) return(NA_character_)
  tokens <- tokens[-1]
  if (length(tokens) > 1 && toupper(tokens[1]) %in% DIRECTIONS) {
    tokens <- tokens[-1]
  }
  if (length(tokens) == 0) return(NA_character_)
  suffix_idx <- which(toupper(tokens) %in% SUFFIXES)
  if (length(suffix_idx) > 0) {
    tokens <- tokens[1:max(suffix_idx)]
  }
  paste(tokens, collapse = " ")
}

homecodes <- bind_rows(lapply(raw$homecodes, function(x) {
  parts <- strsplit(x$homecode, "<br>")[[1]]
  tibble(
    code_id = x$code_id,
    street = extract_street(x$homecode),
    city = trimws(strsplit(parts[2], ",")[[1]][1]),
    lat = as.numeric(x$lat),
    lon = as.numeric(x$lon)
  )
}))
```

With that cleanup done, here are the top 20 streets. **Liberty St** takes
the crown with 21 signs, with Miller Ave right behind at 20.

```{r}
#| label: fig-top20
#| fig-cap: "Top 20 streets by number of registered Summer Game lawn signs (2026)"
#| fig-width: 8
#| fig-height: 6
street_city_counts <- homecodes %>%
  count(street, city, name = "num_signs") %>%
  arrange(desc(num_signs))

top20 <- street_city_counts %>% slice_head(n = 20)

top20 %>%
  mutate(label = paste0(street, " (", city, ")")) %>%
  ggplot(aes(x = reorder(label, num_signs), y = num_signs)) +
  geom_col(fill = "#e8752a") +
  geom_text(aes(label = num_signs), hjust = -0.3, size = 3.5, color = "#33343f") +
  coord_flip() +
  labs(
    x = NULL,
    y = "Number of signs",
    title = "Streets with the most Summer Game signs"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major.y = element_blank(),
    plot.title = element_text(face = "bold", color = "#2e3057")
  ) +
  expand_limits(y = max(top20$num_signs) * 1.1)
```

But hold on -- this ranking has a distortion built in. Liberty St runs
almost the entire width of the city, so of course it accumulates a lot of
signs. A long street with signs spread thinly across two miles beats a
short street packed end-to-end, even though the short street is a far
better place to actually go hunting. And two sign-heavy streets a block
apart get no credit for being part of the same walkable cluster.

## The better question: where's the best 5-minute walk?

What a code hunter really wants to know is: **if I park somewhere and walk
for about five minutes, where does that walk pass the most signs?** The
standard urban-planning rule of thumb for a 5-minute walk is about 400
meters (a quarter mile), so the question becomes: where does a 400m-radius
circle enclose the most signs?

To answer it, I laid a fine grid (50m spacing) over the city and, for every
grid point, counted the signs within 400 meters. That gives a full density
surface -- a heatmap of code-hunting potential. I limited this to Ann Arbor
proper (2,305 of the 2,493 signs); the outlying towns have too few signs to
compete. Three entries with corrupted coordinates in the raw feed (e.g. a
longitude of -2964, which is not a place) were dropped first.

```{r}
#| label: density-grid
# project lat/lon to local meters (equirectangular approx -- accurate to
# well under 1% error at this scale, and much cheaper than great-circle math)
aa <- homecodes %>%
  filter(city == "Ann Arbor", lat > 41.5, lat < 43.5, lon > -85, lon < -83)

lat0 <- mean(aa$lat); lon0 <- mean(aa$lon)
m_per_deg_lat <- 111320
m_per_deg_lon <- 111320 * cos(lat0 * pi / 180)
aa <- aa %>% mutate(x = (lon - lon0) * m_per_deg_lon, y = (lat - lat0) * m_per_deg_lat)

radius <- 400  # meters, ~5 minute walk (standard planning rule of thumb)
grid_res <- 50 # meters, grid spacing
buffer <- 200

gx <- seq(min(aa$x) - buffer, max(aa$x) + buffer, by = grid_res)
gy <- seq(min(aa$y) - buffer, max(aa$y) + buffer, by = grid_res)
grid <- expand.grid(x = gx, y = gy)

# count signs within `radius` of each grid point, via squared-distance
# expansion (a-b)^2 = a^2+b^2-2ab so the cross term can use fast matrix
# multiplication; done in chunks to keep memory bounded (~150k grid points
# x 2,300 signs is too big for one dense distance matrix, but fine in chunks)
px <- aa$x; py <- aa$y
p_sq <- px^2 + py^2
chunk_size <- 5000
counts <- numeric(nrow(grid))
for (start in seq(1, nrow(grid), by = chunk_size)) {
  end <- min(start + chunk_size - 1, nrow(grid))
  gxc <- grid$x[start:end]; gyc <- grid$y[start:end]
  cross <- gxc %*% t(px) + gyc %*% t(py)
  d2 <- outer(gxc^2 + gyc^2, rep(1, length(px))) +
    matrix(p_sq, nrow = length(gxc), ncol = length(px), byrow = TRUE) - 2 * cross
  counts[start:end] <- rowSums(d2 <= radius^2)
}
grid$count <- counts
```

```{r}
#| label: fig-heatmap
#| fig-cap: "Summer Game sign density in Ann Arbor -- color is the number of signs within a 400m (~5 minute) walk; x marks the top 5 distinct hotspots"
#| fig-width: 8
#| fig-height: 7
find_top_hotspots <- function(grid, n = 5, suppress_radius = 2 * radius) {
  remaining <- grid
  hotspots <- list()
  for (i in seq_len(n)) {
    best <- remaining[which.max(remaining$count), ]
    hotspots[[i]] <- best
    d <- sqrt((remaining$x - best$x)^2 + (remaining$y - best$y)^2)
    remaining <- remaining[d > suppress_radius, ]
  }
  bind_rows(hotspots)
}

describe_hotspot <- function(hs_x, hs_y, top_n = 3) {
  d <- sqrt((aa$x - hs_x)^2 + (aa$y - hs_y)^2)
  nearby <- aa[d <= radius, ]
  nearby %>% count(street, sort = TRUE) %>% slice_head(n = top_n) %>% pull(street) %>% paste(collapse = ", ")
}

top5 <- find_top_hotspots(grid, n = 5)
top5$lat <- top5$y / m_per_deg_lat + lat0
top5$lon <- top5$x / m_per_deg_lon + lon0
top5$nearby_streets <- mapply(describe_hotspot, top5$x, top5$y)

grid %>%
  ggplot(aes(x = x, y = y, fill = count)) +
  geom_raster(interpolate = TRUE) +
  scale_fill_viridis_c(name = "Signs within\n400m walk", option = "inferno") +
  geom_point(data = aa, aes(x = x, y = y), inherit.aes = FALSE,
             color = "white", size = 0.15, alpha = 0.35) +
  geom_point(data = top5, aes(x = x, y = y), inherit.aes = FALSE,
             color = "cyan", shape = 4, size = 3, stroke = 1.2) +
  coord_fixed() +
  labs(
    title = "Where a 5-minute walk finds the most signs",
    x = "meters east of city centroid", y = "meters north of city centroid"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold", color = "#2e3057"))
```

The west side glows. To name the winners, I picked the five best distinct
hotspots -- "distinct" matters, because the cells right next to the best
one score nearly as high, so a naive top 5 would just be the same spot five
times. Instead, each time a hotspot is picked, everything within 800m of it
(the distance where two circles stop overlapping) is ruled out before
picking the next.

```{r}
#| label: hotspot-table
top5 %>%
  transmute(
    Rank = row_number(),
    Signs = count,
    `Streets in the circle` = nearby_streets,
    Where = sprintf('<a href="https://www.google.com/maps?q=%.5f,%.5f" target="_blank">open in Google Maps</a>', lat, lon)
  ) %>%
  knitr::kable(escape = FALSE, caption = "The five best 5-minute walks in Ann Arbor, by sign count")
```

The champion is a pocket of the near-west side around **Duncan St, Circle
Dr, and Wines Dr**: 68 signs within a quarter-mile circle. The **Burns
Park** area (Granger Ave,
Brooklyn Ave, Forest Ave) is a whisker behind at 67. Together, the top five
circles hold over 300 signs -- about one of every seven signs in the city,
in five quarter-mile pockets.

::: {.callout-note collapse="true"}
## Sanity check: a cheaper method agrees

The grid scan computes distances from ~150,000 grid points, most of which
aren't near any signs. A cheaper approach only tests circles centered on
the 2,305 actual sign locations -- if signs really cluster, the best circle
is nearly always centered on or next to one. Running that as a
cross-check lands on essentially the same answer: top spot within a couple
hundred meters of the grid scan's, comparable count, same west-side
neighborhoods throughout. The grid scan earns its keep only because it
produces the heatmap.

```{r}
#| label: point-anchored
d2mat <- outer(aa$x, aa$x, "-")^2 + outer(aa$y, aa$y, "-")^2
aa$point_count <- rowSums(d2mat <= radius^2)

top5_points <- find_top_hotspots(
  aa %>% rename(count = point_count), n = 5
)

top5_points %>%
  transmute(Rank = row_number(), Signs = count, `Centered on` = paste0(street, ", ", city)) %>%
  knitr::kable(caption = "Top 5 hotspots, point-anchored method")
```
:::

## Explore the map yourself

The static heatmap shows the overall shape, but planning an actual route is
easier on a map you can pan and zoom. The heat layer below is the same
density idea; the five hotspots are drawn as true 400m circles so you can
see exactly which blocks they cover, and you can toggle on the individual
signs.

```{r}
#| label: interactive-map
library(leaflet)
library(leaflet.extras)

leaflet(aa) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addHeatmap(
    lng = ~lon, lat = ~lat,
    radius = 18, blur = 22, max = 0.15,
    group = "Heatmap"
  ) %>%
  addCircleMarkers(
    lng = ~lon, lat = ~lat,
    radius = 1.5, color = "#2c7fb8", fillOpacity = 0.6, stroke = FALSE,
    popup = ~paste0(street, ", ", city),
    group = "Signs"
  ) %>%
  addCircles(
    data = top5,
    lng = ~lon, lat = ~lat, radius = radius,
    color = "#d95f0e", fillColor = "#fec44f", fillOpacity = 0.15, weight = 2,
    popup = ~paste0("<b>", count, " signs</b> within a 400m walk<br>Near: ", nearby_streets),
    group = "Hotspots"
  ) %>%
  addLayersControl(
    overlayGroups = c("Heatmap", "Signs", "Hotspots"),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  hideGroup("Signs")
```

Happy hunting!

## The fine print

- **Data**: snapshot of the AADL Summer Game map's home-sign feed, pulled
  July 1, 2026. Sign counts change all summer as players register new ones.
- **Privacy**: every location here is one that a player registered on the
  library's sign map on purpose, so that other players would come find it.
  No new information is revealed -- just rearranged.
- **Code**: this whole page is a [Quarto](https://quarto.org) document; every
  chart has a "Show the code" toggle with the R that produced it.
